Analyzing the impact of social attributes on commit integration success

### 2017-02-20 Paper/MSRChallenge2017.tex
revisions up to the evaluation section

\textbf{Comparing two data sets:} We used the social data gathered to create two data 
sets: one with only the technical
factors and the build status, and another with both the technical and social
factors. We performed this split to analyze how well job status be predicted 
by just technical factors, and then with additional social factors.

The data set used in this study~\cite{msr17challenge} is very diverse 
and consists of commits that date from far back. The social data we 
gather is recent, gathered in January 2017. In an effort to mitigate the threat of
using future result to predict previous events,
we removed the commits in the data set that were not performed within the last
three years of the data set's release (2014,2015,2016).  While this is not
perfect, we believe that these numbers are unlikely to have changed
significantly in the last three years.\clg{...did you spot check? Mau's Response: Spot
check that they did belong to those years? Yeah. Zack's Response: assuming you
are asking a different question of if the values changed in the last three
years, than no, we did not check because we weren't sure how.  What should we
say here?}

Since we are interested in the success of the job status of each row, we 
converted the Travis build statuses to just two possible values,
successful (passed in the original provided data set) and not successful 
(errored, failed, canceled
and started in the original data set). We also condensed down all passing and
failing builds in a commit to a single pass or fail for each build status.
At this point we had a 3:1 successful to 
not successful ratio in the rows of the data sets.

>>>>

\textbf{Comparing two data sets:} We used the social data gathered to create two data 
sets: one with only the technical
factors and the build status, and another with both the technical and social
factors. We performed this split to analyze how well technical factors alone,
and then both technical and social
factors predict build integration status.

The data set used in this study~\cite{msr17challenge} is very diverse.
and consists of commits from multiple years ago. The social data we 
gather is recent, gathered in January 2017. In an effort to mitigate the threat of
using future result to predict previous events,
we removed the commits in the data set that were not performed within the last
three years of the data set's release (2014,2015,2016).  While this is not
a perfect solution , we believe that these numbers are unlikely to have changed
significantly in the last three years.\clg{...did you spot check? Mau's Response: Spot
check that they did belong to those years? Yeah. Zack's Response: assuming you
are asking a different question of if the values changed in the last three
years, than no, we did not check because we weren't sure how.  What should we
say here?}

\todo{Zack: Mau, check this first sentence}
Since we are interested in the success of the job status of each commit, we 
converted the Travis build statuses to just two possible values,
successful (passed in the original provided data set) and not successful 
(errored, failed, canceled
and started in the original data set). We also condensed down all passing and
failing builds in a commit to a single pass or fail for each build status.
At this point we had a 3:1 successful to 
not successful ratio in the rows of the data sets.
